---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(kableExtra)

```

## Summary of budget and assets

Assuming the flat sells for `r fmtc(sell_price)`, our total assets are `r fmtc(total_assets)`.  

This is the amount of money we would have in the bank if we sold the flat and paid off the mortgage.

Moving is likely to cost around `r fmtc(moving_cost)`, which means that after moving costs, we will have `r fmtc(total_assets - moving_cost)` before taking out a mortgage.

The purchase price of `r fmtc(buy_price)`, and wanting `r fmtc(bank_money_after_purchase)` in the bank following purchase, we would need a **total mortgage of `r fmtc(buy_price + bank_money_after_purchase + moving_cost - total_assets)`**.

This compares to our current outstanding mortgage of `r fmtc(-current_mortgate_outstanding)`.  The largest mortgage that FirstDirect would give us would be `r fmtc((robin_salary + gemma_salary) * 4.75)`.



## Summary of earnings and spending

### Earnings

Robin's income would be as follows:
- Before tax: `r fmtc(robin_before_tax)`/year, or `r fmtc(robin_before_tax/12)`/month
- After tax: `r fmtc(robin_after_tax)`/year or `r fmtc(robin_after_tax/12)`/month

Gemma's income would be as follows:
- Before tax: `r fmtc(gemma_before_tax)`/year or `r fmtc(gemma_before_tax/12)`/month
- After tax: `r fmtc(gemma_after_tax)`/year or `r fmtc(gemma_after_tax/12)`/month

Total income would be as follows:
- Before tax: `r fmtc(robin_before_tax + gemma_before_tax)`/year or `r fmtc((robin_before_tax + gemma_before_tax)/12)`/month
- **After tax: `r fmtc(robin_after_tax + gemma_after_tax)`/year or `r fmtc((robin_after_tax + gemma_after_tax)/12)`/month**

### Expenditure

Monthly mortgage payments would be `r fmtc(monthly_mortgage_payments)`
Total other payments would be `r fmtc(monthly_spending_nonmortgage)`

Overall spending would be `r fmtc(monthly_mortgage_payments + monthly_spending_nonmortgage)`

### Balance

**Income less spending would be `r fmtc(((robin_after_tax + gemma_after_tax)/12) - (monthly_mortgage_payments + monthly_spending_nonmortgage))`**

## Detailed spending


The following table summarises non-mortgage spending:
```{r echo = FALSE, results = 'asis'}

kable_styling(kable(income_spending, format="html"), bootstrap_options = c("striped","condensed"), font_size = 11, full_width = FALSE, position = "left")
```
## Detailed assets

The following table summarises assets:
```{r echo = FALSE, results = 'asis'}

kable_styling(kable(assets_liabilities, format="html"), bootstrap_options = c("striped","condensed"), font_size = 11, full_width = FALSE, position = "left")
```
